\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-06-26 exps.tex
texts added

By utilizing in-house tools in conjunction with Worst-Case-Execution-Time (WCET)
analyzer \cite{jop:jnl:jsa2007} provided by JOP tools, we were able to estimate
BCRT and WCRT of the following benchmark programs: (full-name?) HRTCS \cite{},
Stepper motor controller (Motor) \cite{}, Robot and Access Environment Control
System (AECS) \cite{}. We have also added a set of customized hardware counters
to the original JOP design in order to collect numbers of clock cycles required for 
logical ticks of given SystemJ program. All examples except Robot are existing
applications translated into pure SystemJ programs. The Robot example models a
combination of robotic arms and conveyors which splits goods based on their
volumetric sizes.

As one can see in Figure \ref{fig:comparison},

>>>>

By utilizing in-house tools in conjunction with Worst-Case-Execution-Time (WCET)
analyzer \cite{jop:jnl:jsa2007} provided by JOP tools, we were able to estimate
BCRT and WCRT of the following benchmark programs: (full-name?) HRTCS \cite{},
Stepper motor controller (Motor) \cite{}, Robot and Access Environment Control
System (AECS) \cite{}. We have also added a set of customized hardware counters
to the original JOP design in order to collect numbers of clock cycles required
for logical ticks of given SystemJ program. All examples except Robot are
existing applications translated into pure SystemJ programs. The Robot example
models a combination of robotic arms and conveyors which splits goods based on
their volumetric sizes. Finally, garbage collector (GC) was disabled in all
experiments to avoid unwanted side-effects such as lengthening clock-domain
logical tick times. Whenever the GC triggers, experiment terminates. BCRT and
WCRT were then calculated based on data collected until that point.

As one can see in Figure \ref{fig:comparison}, BCRT and WCRT were calculated for
all examples. Given the real-time ranges \mbox{\texttt{delay [M..N]}} provided
by programmers, required logical delays \emph{d} were determined by applying the
Algorithm \ref{alg:1}. In HRTCS, real-time delay of the range 50.3..200.3 (ms)
is only satisfied when \emph{d} is between 1506 and 1787 (not shown in Figure).
It is then compiler's job to statically choose one of the values between this
range.

However, it is not the case that given real-time delays in a particular
application are always realizable on JOP. For instance, all other examples other
than HRTCS are required to relax the upper bound for a given real-time delay in
order to obtain a feasible number of \emph{d}. Therefore, Algorithm \ref{alg:2}
is applied to those examples to determine the minimum upper real-time bound
\emph{N} such that there exist a solution for \emph{D} in Algorithm \ref{alg:1}.
Unlike in HRTCS, however, this algorithm gives a unique number for logical tick
delay \emph{d} such that \emph{d} = Min(\emph{$S_2$}) = Max(\emph{$S_1$}).
The compiler, therefore, will choose \emph{d} based on the newly computed \emph{N} for
the examples Robot, Motor and AECS.
